KidsAIR: WMT addresses

### 2020-04-20 dustrak_data_cleaning.Rmd
child data cleaning updates

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "273", location = "WMT")
head(gaps, 25)
head(pm_desc, 25)
tail(pm_desc, 25)

>>>>

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "501", location = "WMT")
head(gaps, 25)
head(pm_desc, 25)
tail(pm_desc, 25)

### 2020-04-20 exposure_models.Rmd
child data cleaning updates

---
title: "KidsAIR: exposure model"
author: "Ethan Walker"
date: "Started 19 March 2020, Updated 13 April 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
input_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/Input/")
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
input_file <- c("exposure_analysis_data_long_new.rds")
output_file <- c("exposure_analysis_data_long_new.rds")

@@

# Linear model
```{r}
subset_model <- lm(log(pm_mean) ~ 
                        income_3level + home_act_smoking + 
                        area, data = exposure_analysis_data_short)

full_model <- lm(log(pm_mean) ~ 
                        education_3level + income_3level + 
                        total_residents_2level + home_floors_2level + home_windows_2level + 
                        stove_age_3level + chimney_clean_3level + 
                        wood_collect_2level + 
                        stove_grade_3level + 
                        home_act_smoking + 
                        moisture_2level + 
                        temp_perc_30_cat +
                        area, data = exposure_analysis_data_short)

summary(subset_model)
r.squaredGLMM(subset_model)

tidy_results <- tidy(full_model)
tidy_results

plot(full_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(full_model), main = "QQ Plot")
```

# Best subsets selection using dredge() from MuMIn
```{r}
options(na.action = "na.fail")

all_subsets <- dredge(full_model, rank = "AIC", extra = c("R^2"))
```

# Linear mixed model with repeated measures
```{r}
subset_model <- lmer(log(pm_mean_daily) ~ 
                        education_3level + income_3level + race_parent_2level + 
                        area + sampling_day + day_of_week +
                        (1 | home), data = exposure_analysis_data_long)

full_model <- lmer(log(pm_mean_daily) ~ 
                        education_3level + income_3level + race_parent_2level + 
                        total_residents_2level + residents_smoke + 
                        home_type_2level + home_floors_2level + home_windows_2level + 
                        stove_age_3level + chimney_clean_3level + home_mold + 
                        home_fireplace + 
                        wood_collect_2level + 
                        stove_grade_3level + 
                        home_act_gas + home_act_propane + home_act_smoking + 
                        moisture_2level + 
                        temp_max_5 + 
                        temp_perc_30_cat +
                        area + sampling_day + day_of_week +
                        (1 | home), data = exposure_analysis_data_long)

summary(full_model)
r.squaredGLMM(full_model)

tidy_results <- tidy(full_model)
tidy_results

plot(full_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(full_model), main = "QQ Plot")
```

>>>>

---
title: "KidsAIR: exposure model"
author: "Ethan Walker"
date: "Started 19 March 2020, Updated 16 April 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      eval = TRUE, include = TRUE)
```

@@

```{r}
# Load individual datasets

input_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/Input/")
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
input_file <- c("exposure_analysis_data_long_new.rds")
output_file <- c("exposure_analysis_data_long_new.rds")

@@

```{r}
# Prep and merge data

####### Format SUMs data to merge with analysis data below
sums_temp_change <- sums_rolling_pm_data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home, sampling_day) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(time_diff = (lead(datetime_sums) - datetime_sums)) %>% 
  mutate(lead_temp = if_else(time_diff < 20, lead(temp_c_sums, 4), lead(temp_c_sums)),
         lead_temp = if_else(time_diff > 25, 999, lead_temp)) %>% 
  replace_with_na(replace = list(lead_temp = 999)) %>% 
  mutate(temp_diff = lead_temp - temp_c_sums,
         # change temp in the following line
         temp_diff_check = if_else(temp_diff >= 5, 1, 0),
         heat_event = if_else(temp_diff_check == 1 & lag(temp_diff_check) == 1, 0,
                              temp_diff_check),
         heat_event = if_else(is.na(temp_diff_check), 1,
                              heat_event)) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(sums_events_sampling_day = sum(heat_event, na.rm = TRUE),
         sums_events_sampling_day_cat = cut(sums_events_sampling_day, 
                                            breaks = c(0, 2, 50),
                           labels = c("<2", "2+"),
                                 right = FALSE)) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  ungroup() %>% 
  select(area:pm_rolling_20, sums_mean_winter:sums_mean_sampling_period,
         time_diff:sums_events_sampling_day_cat) %>% 
  arrange(area, home, sample_date) %>% 
  group_by(home) %>% 
  mutate(sums_events_sampling_period = mean(sums_events_sampling_day, na.rm = TRUE)) %>% 
  select(area, home, home_winter_id, sums_events_sampling_period) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup()

####### Format ambient data to merge with analysis data below
ambient_data <- exposure_analysis_data_long %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(area == "AK") %>% 
  filter(!is.na(sampling_day)) %>% 
  filter(!is.na(sample_date)) %>%
  select(area, home, child_id_char, sample_date, sampling_day, pm_mean_daily,
         zip:mean_temp_roll_4day) %>% 
  group_by(home) %>% 
  mutate(amb_pm_sampling_period_5 = mean(amb_pm_24hr, na.rm = TRUE)/5,
         mean_temp_sampling_period_5 = mean(mean_temp, na.rm = TRUE)/5) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup()

####### Format home activity data to merge with analysis data below
home_activity_data <- exposure_analysis_data_medium %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  group_by(area, home) %>% 
  mutate_at(vars(starts_with("home_act")), as.numeric) %>% 
  mutate_at(vars(starts_with("home_act")), funs(. - 1)) %>% 
  mutate_at(vars(starts_with("home_act")), funs(sum(.))) %>% 
  ungroup() %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  select(home, area, sampling_day, starts_with("home_act"))

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  left_join(sums_temp_change, by = c("area", "home")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home")) %>% 
  select(pm_mean_sampling_period, area, income_3level,  
                 residents_smoke, home_floors_2level, stove_age_3level,  
                 chimney_clean_3level, home_mold, wood_collect_2level, 
                 home_act_door, home_act_smoking, home_act_sweep,
                 stove_grade_3level) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  na.exclude()
```

Initial variables to use for model selection (14) from collinearity RMD:
Demographics: area, income_3level, residents_smoke
Home Characteristics: home_floors_2level, stove_age_3level,
                      chimney_clean_3level, home_mold, wood_collect_2level
Home Activity: home_act_door, home_act_smoking, home_act_sweep
Others: sums_events_sampling_period, mean_temp_sampling_period_5, stove_grade_3level

Note: sums_events_sampling_period and mean_temp_sampling_period_5 have a lot of
missing data and reduce the sample size from 93 to 43. Not considering these
variables for model selection for now.

```{r, include=FALSE}
full_model <- lm(log(pm_mean_sampling_period) ~ area + income_3level + 
                 residents_smoke + home_floors_2level + stove_age_3level + 
                 chimney_clean_3level + home_mold + wood_collect_2level +
                 home_act_door + home_act_smoking + home_act_sweep + 
                 stove_grade_3level,
                 data = analysis_data)

summary(full_model)
r.squaredGLMM(full_model)
tidy(full_model)

plot(full_model)
```

# Best subsets selection using dredge() from MuMIn

Make sure to run `na.exclude` on analysis dataset and `options(na.action = "na.fail")`
before running the dredge best-subsets function below. This will ensure that the 
same dataset is being used for each potential model, which is an assumption and
a prerequisite for comparing different model ranking like AIC.

```{r, eval=FALSE, include=FALSE}
options(na.action = "na.fail")

all_subsets_aic <- dredge(full_model, rank = "AIC", extra = c("R^2"))
all_subsets_aicc <- dredge(full_model, rank = "AICc", extra = c("R^2"))
all_subsets_bic <- dredge(full_model, rank = "BIC", extra = c("R^2"))

write_rds(all_subsets_aic, paste0(output_path, "Output/all_subsets_aic"))
write_rds(all_subsets_aicc, paste0(output_path, "Output/all_subsets_aicc"))
write_rds(all_subsets_bic, paste0(output_path, "Output/all_subsets_bic"))
```

```{r}
all_subsets_aic <- read_rds(paste0(output_path, "Output/all_subsets_aic"))
all_subsets_aicc <- read_rds(paste0(output_path, "Output/all_subsets_aicc"))
all_subsets_bic <- read_rds(paste0(output_path, "Output/all_subsets_bic"))

head(all_subsets_aic, 10)
head(all_subsets_aicc, 10)
head(all_subsets_bic, 10)
```

```{r}
subset_model <- lm(log(pm_mean_sampling_period) ~ 
                   income_3level + home_act_door + residents_smoke, 
                   data = analysis_data)

summary(subset_model)
#tidy(subset_model)

plot(subset_model)
```

### 2020-04-20 wmt_addresses.Rmd
child data cleaning updates

---
title: "KidsAIR: WMT addresses"
author: "Ethan Walker"
date: "Started 3 April 2020, Updated 3 April 2020"
output: pdf_document
---

@@

```{r}
wmt_addresses <- read_xlsx("Input/WMT/wmt_addresses.xlsx")

@@

```{r}
addresses_geocoded <- geocode(location = addresses_new$address, output = "latlon",
                              source = "google")
```

>>>>

---
title: "KidsAIR: WMT addresses"
author: "Ethan Walker"
date: "Started 3 April 2020, Updated 17 April 2020"
output: pdf_document
---

@@

```{r}
input_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

wmt_addresses <- read_xlsx(paste0(input_path, "Input/WMT/wmt_addresses.xlsx"))

@@

```{r}
addresses_geocoded <- addresses_new %>% 
  mutate_geocode(location = address, output = "more",
                              source = "google")
```

```{r}
wmt_map <- map_data("state") %>% 
  filter(region == "montana")

wmt_homes <- addresses_geocoded %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "azure", size = 1.2) +
    geom_point(data=addresses_geocoded, 
             aes(lon, lat), size = 3) +
    theme_void() +
    labs(title = "WMT Homes Mapped", subtitle = "Geocoded from addresses") 
wmt_homes
```
